---
title: "A7"
format: html
editor: visual
---

## Q3

```{r}
#| echo: FALSE
#| message: FALSE
#| warning: FALSE

library(tidyverse)
library(data.table) ## For the fread function
library(lubridate)

source("sepsis_monitor_functions.R")
library(tictoc)
library(googledrive)
```

```{r}
#| echo: FALSE
#| message: FALSE
#| warning: FALSE

# ## Calling drive_deauth() prevents R from trying to authenticate via a browser
drive_deauth()
file_link <- "https://drive.google.com/file/d/1HhW3s_zLFCxxzBqVIPUO5-B60a4ac6r0/view?usp=share_link"
# 
## All data up until now
new_data <- updateData(file_link)

# new_data <- read.csv("sepsis_data.csv")

## Include only most recent data
most_recent_data <- new_data %>%
  group_by(PatientID) %>%
  filter(obsTime == max(obsTime))
```

## Date and Time `r Sys.time()`

## A table listing the patients who currently have sepsis (if any), along with their most recent heart rate, temperature, and respiratory rate

```{r}

#| echo: FALSE
#| message: FALSE
#| warning: FALSE

# A table listing the patients who currently have sepsis (if any)
sepsis_patients <- most_recent_data %>%
  filter(SepsisLabel == 1) %>%
  select(PatientID, HR, Temp, Resp)

library(DT)
datatable(sepsis_patients)
```

## Plots for all patients who have sepsis (if any) that show the complete history of their heart rate, temperature, and respiratory rate during their time in the ICU.

```{r}
#| echo: FALSE
#| message: FALSE
#| warning: FALSE
library(cowplot)
sepsis_patients <- most_recent_data %>%
  filter(SepsisLabel == 1) %>%
  select(PatientID, HR, Temp, Resp)

### "001118" "004939" "007540"
###"007540" Temperature: NA

sepsis_patients_ids <- unique(sepsis_patients$PatientID)
patient_plots <- list()

for (patient in sepsis_patients_ids) { 
  patient_data <- new_data %>%
    filter(PatientID == patient) %>%
    select(ICULOS, HR, Temp, Resp)
  
  p1 <- ggplot(patient_data, aes(x = ICULOS, y = HR)) +
    geom_line() +
    ggtitle(paste0("Heart Rate for Patient ", patient)) +
    theme_minimal() +
    xlab("ICU Length of Stay (hours)") +
    ylab("Heart Rate")
  
  p2 <- ggplot(patient_data, aes(x = ICULOS, y = Temp)) +
    geom_line() +
    ggtitle(paste0("Temperature for Patient ", patient)) +
    theme_minimal() +
    xlab("ICU Length of Stay (hours)") +
    ylab("Temperature")
  
  p3 <- ggplot(patient_data, aes(x = ICULOS, y = Resp)) +
    geom_line() +
    ggtitle(paste0("Respiratory Rate for Patient ", patient)) +
    theme_minimal() +
    xlab("ICU Length of Stay (hours)") +
    ylab("Respiratory Rate")
  
  patient_plots[[patient]] <- list(p1, p2, p3)
}

# Arrange plots in a grid
plot_grid(plotlist = unlist(patient_plots, recursive = FALSE),
          ncol = 3, labels = "AUTO", label_size = 12)

```

## A table showing the change in heart rate, temperature, and respiratory rate between the last two measurements for all patients

```{r}
#| echo: FALSE
#| message: FALSE
#| warning: FALSE
change_data <- new_data %>%
  group_by(PatientID) %>%
  arrange(PatientID, ICULOS) %>%
  slice_tail(n = 2) %>%
  mutate(across(c(HR, Temp, Resp), list(change = ~ . - lag(.)))) %>%
  filter(!is.na(HR_change) | !is.na(Temp_change) | !is.na(Resp_change)) %>%
  select(PatientID, HR_change, Temp_change, Resp_change) %>%
  pivot_longer(cols = c(HR_change, Temp_change, Resp_change), names_to = "variable", values_to = "change") %>%
  mutate(change_direction = case_when(change > 0 ~ "increased",
                                      change < 0 ~ "decreased",
                                      TRUE ~ "same"))

datatable(change_data)

```
